False Positive Probabilities for all Kepler Objects of Interest: \\ \nvalnew\ newly validated planets and \nfpnew\ likely false positives

### 2016-01-05 ms.tex
updated HZ table, added acknowledgments, blended planet discussion

\newcommand{\nreliable}{2823} %from figure
\newcommand{\nval}{1997} %from figure
\newcommand{\nreliableFP}{398} %from figure
\newcommand{\nvalnew}{1325} %from pie chart
\newcommand{\nfpnew}{424}  % all candidate with FPP < 0.9
\newcommand{\ncurval}{984} % from pie chart

@@

@@

The \vespa\ procedure models an eclipse signal as a simple trapezoid,
parametrized by depth $\delta$, total duration $T$, and shape
parameter $T / \tau$, where $\tau$ is the ``ingress/egress'' duration
(such that a completely V-shaped transit has $T/\tau = 2$).  For the
transit signal being evaluated, the joint posterior probability
density function (PDF) of these shape parameters is sampled with
Markov Chain Monte Carlo (MCMC), using the \texttt{emcee} sampler
\citep{emcee}.  This allows the likelihood for each hypothesis to be
determined by simulating a physically realistic population of the
hypothesized astrophysical scenario and using this population to
define the PDF for the trapezoidal parameters under the hypothesis.
The likelihood is then \begin{equation}   \eqlabel{lhood}   \mathcal
L_i = \displaystyle \int p_\mathrm{sig}\left(\bvec{\theta}\right)
p_i\left(\bvec{\theta}\right)\,d\bvec{\theta}, \end{equation} where
$\bvec{\theta}$ is the vector of trapezoidal shape parameters,
$p_\mathrm{sig}$ is the posterior PDF of the signal, and $p_i$ is the
PDF for the parameters under hypothesis $i$.\footnote{$\mathcal L_i$
may be seen to be the ``evidence'' or ``marginalized likelihood'' of
the trapezoidal model under hypothesis $i$, with $p_\mathrm{sig}$
being the likelihood and $p_i$ being the prior, integrated over the
$\bvec{\theta}$ parameter space.  But for clarity, and for continuity
with previous publications, we continue to call $\mathcal L_i$ the
``likelihood'' for hypothesis $i$.}  The hypotheses supported by
\vespa\ are the following: unblended eclipsing binary (EB),
hierarchical- triple eclipsing binary (HEB), chance-aligned
background/foreground eclipsing binary (BEB), and transiting planet
(Pl).  In this work, we also implement ``double-period'' versions of
each of the stellar false positive scenarios, acknowledging the
possibility that if an eclipsing binary has similar primary and
secondary eclipse depths, then it might be mischaracterized as a
primary-only transiting planet signal at twice the orbital period
(especially if diluted).  We note that the determination of the
diluted eclipse depth of all these blended scenarios assumes that the
light from the blended system is \emph{fully contained} within the
target's photometric aperture.  That is, these scenarios do not
account for the possibility that only a small fraction of the light
from a nearby contaminating star might be in the aperture, many of
which have already been identified via other methods
\cite{Bryson:2013,Coughlin:2014}.

@@

The most substantial difference between the current implementation of
\vespa\ and the procedure documented in \citetalias{Morton:2012} is
how stellar properties are treated.  Previously, either the target
star's mass and radius were explicitly provided, or they were randomly
generated according to the stellar population expected along the line
of sight by the TRIdimensional modeL of thE GALaxy (TRILEGAL) Galactic
stellar popultion synthesis tool, but constrained to agree with some
observed color(s) of the star (e.g. $J-K$), to within some specified
tolerance.  This strategy was used both to generate the host stars for
the transiting planet model and the binary and triple stars for the EB
and HEB false positive models.

@@

Of these KOIs with reliable \vespa\ FPPs, \nval\ have ${\rm FPP}
<0.01$, and are thus validated at the 99\% level.  These KOIs are
marked as labeled as such in \tab{fpp}.  These are not all new
validations, however, since a number of them are already CONFIRMED.
\Fig{fpppie} shows a different kind of summary, grouping KOIs by
disposition and splitting up the CANDIDATES according to the \vespa\
results, showing that \nvalnew\ KOIs are newly validated at the 99\%
level. \Fig{rpcand} shows the radii and periods of the CANDIDATE KOIs,
grouped by FPP.

@@

One final note about these calculations is that unidentified transit
timing variations (TTVs) will increase the FPP of a transit signal, as
the shape of the folded light curve will be distorted, typically
resulting in a longer signal which a trapezoid model will also
identify as more V-shaped.  While we have analyzed light curves
correcting for known TTVs when available, we have also undoubtedly
missed many systems with as-yet-unspecified TTV signals.  This means
that a large FPP may be simply an indication of unidentified TTVs
rather than an astrophysical false positive, especially in  
multi-planet systems, which should overall have a very low false positive
rate \citep{Lissauer:2014,Rowe:2014}.  It is thus probable that
despite multi-KOIs having lower FPPs than singles (\tab{meanFPP}),
even these relatively low FPPs are inflated by the effect of TTVs.
\Tab{fpp} lists whether known TTV were accounted for when constructing
the folded transit light curve for each KOI.

@@

Thus, we expect only about 0.4\% (4/980) of unidentified PEMs to end
up as validated according to \vespa. As the total rate of PEMs is
estimated to be something around 35\% \citep{Coughlin:2014}, there
remains a small ($\sim$0.1\%  chance) that any of the validated
planets may turn out to be due to  as-yet unidentified contamination
from one of the false positive  sources that cause PEMs.  In other
words, among our validated sample of planets, there may well be one or
two that turn out to be false positives due to distant contamination
(such as via the ``column anomaly'' effect), but not substantially
more.

@@

@@

\subsection{The enigmatic case of KOI-6705.01}

@@

While previous \emph{a priori} false positive rate estimates
\citep{Morton:2011b,Fressin:2013} have made clear that the \kepler\
planet candidate catalogs are generally low enough to ignore for the
purposes of planet occurrence rate calculations, any more detailed
study of any small subset of individual KOIs should understand in more
detail the FPPs of those specific candidates.  This type of small-sample 
candidate culling using individually calculated FPPs has
already been done in the literature
\citep{MortonSwift:2014,MortonWinn:2014}; the publication of this full
catalog allows the community to do the same.  In particular, several
other studies have shown that specific samples of KOIs tend to have
large FPPs than the global average, so studies involving giant-planet
KOIs \citep{Santerne:2015} or evolved stars \citep{Sliski:2014} are in
even greater need of the individual FPP analysis here presented.

@@

\acknowledgments
TDM acknowledges support from the \kepler\ Participating Scientist
Program (NNX14AE11G). \ldots

@@

\begin{figure*}[p]
\begin{center}
\includegraphics[width=7in]{figures/RP_cand.pdf}
\end{center}
\caption{Periods and radii of KOIs with CANDIDATE disposition, grouped
  by FPP value.  Green circles are most likely to be planets, red X's
  are most likely to be false positives, and blue plusses have
  intermediate FPPs.  Grey dots are KOIs for which the
  \vespa\ calculation is considered less reliable.  
  \figlabel{rpcand}}
\end{figure*}

>>>>

\newcommand{\nreliable}{2823} %from figure
\newcommand{\nval}{1997} %from figure
\newcommand{\nreliableFP}{398} %from figure
\newcommand{\nvalnew}{1325} %from pie chart
\newcommand{\nfpnew}{424}  % all candidate with FPP < 0.9
\newcommand{\ncurval}{984} % from pie chart
\newcommand{\nhz}{10}

@@

%from Natalie
\newcommand{\teff}{\ensuremath{T_{\rm eff}}}
\newcommand{\logg}{\ensuremath{\log{g}}}
\newcommand{\vsini}{\ensuremath{v \sin{i}}}
\newcommand{\feh}{[Fe/H]}
\newcommand{\logl}{\ensuremath{\log{L}}}

\newcommand{\rsun}{\ensuremath{R_\sun}}
\newcommand{\msun}{\ensuremath{M_\sun}}
\newcommand{\lsun}{\ensuremath{L_\sun}}

\newcommand{\rstar}{\ensuremath{R_\star}}
\newcommand{\mstar}{\ensuremath{M_\star}}
\newcommand{\loggstar}{\ensuremath{\logg_\star}}
\newcommand{\lstar}{\ensuremath{L_\star}}
\newcommand{\astar}{\ensuremath{a_\star}}
\newcommand{\dstar}{\ensuremath{d_\star}}
\newcommand{\loglstar}{\ensuremath{\log{L_\star}}}
\newcommand{\rhostar}{\ensuremath{\rho_\star}}

\newcommand{\rpl}{\ensuremath{R_{\rm P}}}
\newcommand{\mpl}{\ensuremath{M_{\rm P}}}
\newcommand{\lpl}{\ensuremath{L_{\rm P}}}
\newcommand{\rhopl}{\ensuremath{\rho_{\rm P}}}
\newcommand{\loggpl}{\ensuremath{\logg_{\rm P}}}
\newcommand{\teq}{\ensuremath{T_{\rm eq}}}

\newcommand{\rjup}{\ensuremath{R_{\rm J}}}
\newcommand{\mjup}{\ensuremath{M_{\rm J}}}
\newcommand{\rhojup}{\ensuremath{\rho_{\rm J}}}
\newcommand{\rearth}{\ensuremath{R_{\earth}}}
\newcommand{\mearth}{\ensuremath{M_{\earth}}}

\newcommand{\msini}{\ensuremath{m \sin{i}}}
\newcommand{\mplsini}{\ensuremath{\mpl\sin{i}}}

@@

The \vespa\ procedure models an eclipse signal as a simple trapezoid,
parametrized by depth $\delta$, total duration $T$, and shape
parameter $T / \tau$, where $\tau$ is the ``ingress/egress'' duration
(such that a completely V-shaped transit has $T/\tau = 2$).  For the
transit signal being evaluated, the joint posterior probability
density function (PDF) of these shape parameters is sampled with
Markov Chain Monte Carlo (MCMC), using the \texttt{emcee} sampler
\citep{emcee}.  This allows the likelihood for each hypothesis to be
determined by simulating a physically realistic population of the
hypothesized astrophysical scenario and using this population to
define the PDF for the trapezoidal parameters under the hypothesis.
The likelihood is then \begin{equation}   \eqlabel{lhood}   \mathcal
L_i = \displaystyle \int p_\mathrm{sig}\left(\bvec{\theta}\right)
p_i\left(\bvec{\theta}\right)\,d\bvec{\theta}, \end{equation} where
$\bvec{\theta}$ is the vector of trapezoidal shape parameters,
$p_\mathrm{sig}$ is the posterior PDF of the signal, and $p_i$ is the
PDF for the parameters under hypothesis $i$.\footnote{$\mathcal L_i$
may be seen to be the ``evidence'' or ``marginalized likelihood'' of
the trapezoidal model under hypothesis $i$, with $p_\mathrm{sig}$
being the likelihood and $p_i$ being the prior, integrated over the
$\bvec{\theta}$ parameter space.  But for clarity, and for continuity
with previous publications, we continue to call $\mathcal L_i$ the
``likelihood'' for hypothesis $i$.}  The hypotheses supported by
\vespa\ are the following: unblended eclipsing binary (EB),
hierarchical-triple eclipsing binary (HEB), chance-aligned
background/foreground eclipsing binary (BEB), and transiting planet
(Pl).\footnote{We note that we do not consider ``blended transiting planet''
false positive scenarios, either due to physically associated or 
chance-aligned companions.  See \sect{btp} for more discussion.} 
In this work, we also implement ``double-period'' versions of
each of the stellar false positive scenarios, acknowledging the
possibility that if an eclipsing binary has similar primary and
secondary eclipse depths, then it might be mischaracterized as a
primary-only transiting planet signal at twice the orbital period
(especially if diluted).  We note that the determination of the
diluted eclipse depth of all these blended scenarios assumes that the
light from the blended system is \emph{fully contained} within the
target's photometric aperture.  That is, these scenarios do not
account for the possibility that only a small fraction of the light
from a nearby contaminating star might be in the aperture, many of
which have already been identified via other methods
\cite{Bryson:2013,Coughlin:2014}.

@@

The most substantial difference between the current implementation of
\vespa\ and the procedure documented in \citetalias{Morton:2012} is
how stellar properties are treated.  Previously, either the target
star's mass and radius were explicitly provided, or they were randomly
generated according to the stellar population expected along the line
of sight by the TRIdimensional modeL of thE GALaxy (TRILEGAL) Galactic
stellar population synthesis tool, but constrained to agree with some
observed color(s) of the star (e.g. $J-K$), to within some specified
tolerance.  This strategy was used both to generate the host stars for
the transiting planet model and the binary and triple stars for the EB
and HEB false positive models.

@@

\subsection{Validation of \nvalnew\ new planets}

While the FPP below which to claim planet validation is clearly
an arbitrary choice, there is precedent to using ${\rm FPP} <0.01$ as 
the threshold---\citet{Rowe:2014} validated over 800 multi-planet KOIs
using this number.  Adopting this same threshold, we find that 
of the KOIs with reliable \vespa\ FPPs, \nval\ have ${\rm FPP}
<0.01$, and are thus validated at the 99\% level.  
These KOIs are labeled as such in \tab{fpp}.  These are not all new validations,
however, since a number of them are already CONFIRMED. \Fig{fpppie}
shows a different kind of summary, grouping KOIs by disposition and
splitting up the CANDIDATES according to the \vespa\ results, showing
that \nvalnew\ KOIs are newly validated at the 99\% level.
\Fig{rpcand} shows the radii and periods of the CANDIDATE KOIs,
grouped by FPP.

%HZ table
\input{table_hz}

As there is significant interest in identifying potentially habitable
planets, \tab{hz} lists the properties of \nhz\ CANDIDATE KOIs newly
validated by this work that \textit{may} fall within the optimistic
habitable zones of their host stars \citep{Kopparapu:2013}, 
according to the stellar
properties reported by the DR24 table at the NExScI Archive.  We note
that while more detailed follow-up observations (imaging and
spectroscopy) have been taken for each of these targets, we make no
attempt here to characterize these systems in detail.  Analysis of
high-resolution spectroscopy in particular will solidify the
properties of these host stars, which will affect the habitable zone
boundaries.  We thus emphasize that this list is neither complete nor
final, serving only to draw attention to new validations of 
interest rather than to be a definitive statement on potential 
habitability.  We also note that based solely on the properties in the 
DR24 table, KOI-5475.01 (listed as having a 448-day orbital period) 
should also be included in this list of potentially habitable-zone
planets.  However, as explained in \citet[][Section 5.5.4]{Coughlin:2015},
this particular KOI actually has a 224-day period, making its insolation
to high to be within the habitable zone; we have thus excluded it 
from \tab{hz}.

\subsection{Likely False Positives}

@@

One final note about these calculations is that unidentified transit
timing variations (TTVs) will increase the FPP of a transit signal, as
the shape of the folded light curve will be distorted, typically
resulting in a longer signal which a trapezoid model will also
identify as more V-shaped.  While we have analyzed light curves
correcting for known TTVs when available, we have also undoubtedly
missed many systems with as-yet-unspecified TTV signals.  This means
that a large FPP may be simply an indication of unidentified TTVs
rather than an astrophysical false positive, especially in  
multi-planet systems, which should overall have a very low false positive
rate \citep{Lissauer:2014,Rowe:2014}.  It is thus probable that
despite multi-KOIs having lower FPPs than singles (\tab{meanFPP}),
even these relatively low FPPs are inflated by the effect of TTVs.
\Tab{fpp} lists whether known TTVs were accounted for when constructing
the folded transit light curve for each KOI.

@@

Thus, we expect only about 0.4\% (4/980) of unidentified PEMs to end
up as validated according to \vespa. As the total rate of PEMs is
estimated to be something around 35\% \citep{Coughlin:2014}, there
remains a small ($\sim$0.1\%  chance) that any of the validated
planets may turn out to be due to  as-yet unidentified contamination
from one of the false positive  sources that cause PEMs.  In other
words, among our validated sample of planets, there may well be one or
two that turn out to be false positives due to distant contamination
(such as via the ``column anomaly'' effect), but not substantially
more.  (See \sect{gaidos} for an example of a KOI caused by a 
column anomaly that went unidentified by the \kepler\ pipeline but
which \vespa\ assigned a high FPP.)

@@

\subsection{Blended Transiting Planets?}
\sectlabel{btp}

In this work, the only false positive scenarios we consider are 
eclisping binary stars (EB, HEB, BEB, and the double-period versions
thereof).  Previous work studying \kepler\ false positive rates
\citep[e.g.][]{Fressin:2013} has also considered the  ``blended transiting
planet'' to be a false positive---i.e.,  a fainter companion
star hosting a transiting planet larger than what would be inferred if
it were transiting the target star.  Because we do not consider such
a scenario to be a false positive, the \vespa\ analysis presented here 
does not quantify its probability.  As a result, we are \textit{not}
able to unambiguously determine the radii of the planets we validate---
all the planet radii listed in \tab{fpp} are based on the assumption
that the planet transits the target star and that the target star is 
unblended.  If the target star is actually a member of an unresolved
binary system (as a significant fraction of KOIs undoubtedly are),
then the true planet radius will be larger (significantly larger 
if transiting a fainter companion).  This was indeed the motivation
for \citet{Fressin:2013} to consider the ``blended transiting planet''
as a false positive; part of the goal of that work was to 
compute the planet occurrence rates in different radius bins.  
However, trying to distinguish between single and binary target
star configurations is beyond the scope of this work; we thus follow
the precedent of \citet[][especially Section 5]{Lissauer:2014} by 
acknowledging the potential for substantial radius
uncertainties among the validated planet sample while nevertheless 
defending the validations themselves as robust.

@@

\subsection{The enigmatic case of KOI-6705.01}
\sectlabel{gaidos}

@@

While previous \emph{a priori} false positive rate estimates
\citep{Morton:2011b,Fressin:2013} have made clear that the \kepler\
planet candidate catalogs are generally low enough to ignore for the
purposes of planet occurrence rate calculations, any more detailed
study of any small subset of individual KOIs should understand in more
detail the FPPs of those specific candidates.  This type of small-sample 
candidate culling using individually calculated FPPs has
already been done in the literature
\citep{MortonSwift:2014,MortonWinn:2014}; the publication of this full
catalog allows the community to do the same.  In particular, several
other studies have shown that specific samples of KOIs tend to have
larger FPPs than the global average, so studies involving giant-planet
KOIs \citep{Santerne:2015} or evolved stars \citep{Sliski:2014} are in
even greater need of the individual FPP analysis here presented.

@@

\acknowledgments TDM acknowledges support from the \kepler\
Participating Scientist Program (NNX14AE11G). This paper includes data
collected by the \kepler\ mission. Funding for the \kepler\ mission
is provided by the NASA Science Mission directorate. The authors
acknowledge the efforts of the \kepler\ Mission team for obtaining
the light curve products used in
this publication, which were generated by the \kepler\ Mission
science pipeline through the efforts of the \kepler\ Science
Operations Center and Science Office. The \kepler\ Mission is led by
the project office at NASA Ames Research Center. Ball Aerospace built
the \kepler\ photometer and spacecraft which is operated by the
mission operations center at LASP. These data products are archived at
the NASA Exoplanet Science Institute, which is operated by the
California Institute of Technology, under contract with the National
Aeronautics and Space Administration under the Exoplanet Exploration
Program. This research has made use of NASA's Astrophysics Data
System.

@@

\begin{figure*}[p]
\begin{center}
\includegraphics[width=7in]{figures/RP_cand.pdf}
\end{center}
\caption{Periods and radii of KOIs with CANDIDATE disposition, grouped
  by FPP value.  Green circles are most likely to be planets, red X's
  are most likely to be false positives, and blue plusses have
  intermediate FPPs.  Grey dots are KOIs not identified as likely 
  false positives for which the
  \vespa\ calculation is considered less reliable.  
  \figlabel{rpcand}}
\end{figure*}
